Evolution of ORM Systems: Formal Foundations

### 2013-01-09 doc/description.tex
orm mapping works with collections

\begin{align*}
	\mathbf{\rho_p} : Property* \rightarrow Column* \\ \\
	\rho_{sp}(p) = \begin{cases}
		\inference{p = \varnothing}{\varnothing}\\
		\inference{|p| > 1}{\rho_{sp}(head(p)) \cup \rho_{sp}(tail(p))}\\\\
 		\inference{cardinality(p) = 1 \wedge !\;mandatory(p)
 			\\ \wedge \exists t : t = table(name(owningClass(p)), d) 
		 }{\begin{gathered}
	  		column(name(p), \rho_t(type(p)), \varnothing )
		\end{gathered}} \\ \\
  		\inference{cardinality(p) = 1 \wedge mandatory(p)
			 \\ \wedge \exists t : t = table(name(owningClass(p)), d)
			\\ \wedge \not instanciated(owningClass(p))
		}{\begin{gathered}
 	 		column(name(p), \rho_t(type(p)), NOTNULL ) \\ 
		\end{gathered}}
 	\end{cases}
\end{align*}
\begin{align*}
	\mathbf{\rho_p} : Property* \rightarrow Table* \\ \\
	\rho_{cp}(p) = \begin{cases}
 	\inference{cardinality(p) > 1 \wedge !\;mandatory(p) \\ 
 		\wedge 	\exists t : t = table(name(owningClass(p)), d)
 		}{\begin{gathered}
 			table(name(p), primaryKey("Id"), \\ column("value", 			\rho_t(type(p)), \varnothing), \\ foreignKey(name(p), 			name(owningClass(p)), NOTNULL) \\
	\end{gathered}}\\ \\
 	\inference{ cardinality(p) > 1 \wedge mandatory(p) \\ 
 		\wedge \exists t : t = table(name(owningClass(p)), d) 
 		}{\begin{gathered}  
 			table(name(p), primaryKey("Id"), \\ 
 			column("value", \rho_t(type(p)), NOTNULL), \\ 			foreignKey(name(p), name(owningClass(p)), NOTNULL)
	 \end{gathered}}
 	\end{cases}
\end{align*}

@@

\begin{align*}
	\mathbf{\rho_a} : Association* \rightarrow ForeignKey* \\
	\rho_a(a) = \begin{cases}
		\inference{ startCardinality(a) = 0 \\ \wedge \exists t : t = table(name(owningClass(p)), d) \\ \wedge \exists u : u = table(reference(a)), d)
		}{
			foreignKey(name(a), name(t),  \varnothing) 
	 	}
  \\ \\
 	 \inference{ startCardinality(a) = 1 \\ \wedge \exists t : t = table(name(owningClass(p)), d) \\ \wedge \exists u : u = table(reference(a)), d)
 	 }{ 
		foreignKey(name(a), name(t),  NOTNULL)
	}
	 \end{cases}
\end{align*}
\begin{align*} 
	\mathbf{\rho_a} : Association* \rightarrow Table* \\
  	\rho_a(a) = \inference{  startCardinality > 1 \\ \wedge \rho(owningClass(p)) \in tables(d) \wedge \rho(reference(a)) \in tables(d)
  		}{\begin{gathered}  
		 table(name(a), pk("Id"), \varnothing, \\ foreignKey(owningClass(a),owningClass(a), NOTNULL) \\ foreignkey(reference(a), reference(a), NOTNULL)) 
  		\end{gathered}}  
\end{align*}

>>>>

\begin{align*}
	\mathbf{\rho_p} : Property* \rightarrow Column* \\ \\
	\rho_{sp}(p) = \begin{cases}
		\inference{p = \varnothing}{\varnothing}\\
		\inference{|p| > 1}{\rho_{sp}(head(p)) \cup \rho_{sp}(tail(p))}\\\\
 		\inference{cardinality(p) = 1 \wedge !\;mandatory(p)
 			\\ \wedge \exists t : t = table(name(owningClass(p)), d) 
		 }{\begin{gathered}
	  		column(name(p), \rho_t(type(p)), \varnothing )
		\end{gathered}} \\ \\
  		\inference{cardinality(p) = 1 \wedge mandatory(p)
			 \\ \wedge \exists t : t = table(name(owningClass(p)), d)
			\\ \wedge \not instanciated(owningClass(p))
		}{\begin{gathered}
 	 		column(name(p), \rho_t(type(p)), NOTNULL ) \\ 
		\end{gathered}}
 	\end{cases}
\end{align*}
\begin{align*}
	\mathbf{\rho_p} : Property* \rightarrow Table* \\ \\
	\rho_{cp}(p) = \begin{cases}
		\inference{p = \varnothing}{\varnothing}\\
		\inference{|p| > 1}{\rho_{cp}(head(p)) \cup \rho_{cp}(tail(p))}\\\\
     	\inference{cardinality(p) > 1 \wedge !\;mandatory(p) \\ 
     		\wedge 	\exists t : t = table(name(owningClass(p)), d)
     		}{\begin{gathered}
     			table(name(p), primaryKey("Id"), \\ column("value", 			\rho_t(type(p)), \varnothing), \\ foreignKey(name(p), 			name(owningClass(p)), NOTNULL) \\
    	\end{gathered}}\\ \\
     	\inference{ cardinality(p) > 1 \wedge mandatory(p) \\ 
     		\wedge \exists t : t = table(name(owningClass(p)), d) 
     		}{\begin{gathered}  
     			table(name(p), primaryKey("Id"), \\ 
     			column("value", \rho_t(type(p)), NOTNULL), \\ 			foreignKey(name(p), name(owningClass(p)), NOTNULL)
    	 \end{gathered}}
 	\end{cases}
\end{align*}

@@

\begin{align*}
	\mathbf{\rho_a} : Association* \rightarrow ForeignKey* \\
	\rho_a(a) = \begin{cases}
		\inference{a = \varnothing}{\varnothing}\\
		\inference{|a| > 1}{\rho_{a}(head(a)) \cup \rho_{a}(tail(a))}\\\\
		\inference{ startCardinality(a) = 0 \\ \wedge \exists t : t = table(name(owningClass(p)), d) \\ \wedge \exists u : u = table(reference(a)), d)
		}{
			foreignKey(name(a), name(t),  \varnothing) 
	 	}
  \\ \\
 	 \inference{ startCardinality(a) = 1 \\ \wedge \exists t : t = table(name(owningClass(p)), d) \\ \wedge \exists u : u = table(reference(a)), d)
 	 }{ 
		foreignKey(name(a), name(t),  NOTNULL)
	}
	 \end{cases}
\end{align*}
\begin{align*} 
	\mathbf{\rho_a} : Association* \rightarrow Table* \\
	\rho_a(a) = \begin{cases}
 		\inference{a = \varnothing}{\varnothing}\\
		\inference{|a| > 1}{\rho_{a}(head(a)) \cup \rho_{a}(tail(a))}\\\\
		\inference{  startCardinality > 1 \\ \wedge \rho(owningClass(p)) \in tables(d) \wedge \rho(reference(a)) \in tables(d)
  		}{\begin{gathered}  
		 table(name(a), pk("Id"), \varnothing, \\ foreignKey(owningClass(a),owningClass(a), NOTNULL) \\ foreignkey(reference(a), reference(a), NOTNULL)) 
  		\end{gathered}}  
 	\end{cases}
\end{align*}
